%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Director of Engineering} % Title
    {Lightspeed Venture Partners} % Organization
    {Menlo Park, CA} % Location
    {Jan. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Leading the data platform engineering team at Lightspeed to create best-in-class data solutions to power data-driven deal sourcing, diligence and portfolio support in VC investing}
        \begin{itemize}[label=$\circ$]
          \item{Building automated and scalable data infrastructure to onboard datasets, generate features, train and test machine learning models to power our various data platform functions}
          \item{Creating internal tools to help track and analyze relationships and signals on future investment candidates and opportunities}
          \item{Working cross-functionally with investors to improve the ability of our data models to generate useful business insights}
        \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Staff Software Engineer, Machine Learning \& Intelligence, Autonomous Vehicle Division} % Title
    {Lyft Inc.} % Organization
    {San Francisco, CA} % Location
    {Jun. 2018 - Jan. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Built the machine learning pipeline for the Mapping Intelligence team in the Autonomous Vehicle Division to iterate on computer vision models to build High Definition maps}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Staff Software Engineer} % Title
    {} % Organization
    {} % Location
    {Aug. 2017 - May 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Led a team of three engineers to rebuild Lyft's live traffic profile estimation pipeline to reduce overall latency from hours to less than 30 minutes}
        \item{Collaborated with ETA Data Science team to reduce Lyft's ETA estimation error rate by 5\%}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Principal Software Engineer} % Title
    {Walmart Labs} % Organization
    {Sunnyvale, CA} % Location
    {Aug. 2016 - Apr. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Led a team of three engineers to re-architect and build the Walmart Ad Exchange (WMX) platform on Apache Spark to drive smart and responsive ad-targeting based on Walmart’s unique offline+online datasets}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Title
    {Netflix Inc.} % Organization
    {Los Gatos, CA} % Location
    {Aug. 2014 - Jul. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Built and launched the first production grade Apache Spark based machine learning pipeline at Netflix}
          \begin{itemize}[label=$\circ$]
            \item{Enabled rapid development of algorithms to rank recommendations of movies and TV shows on Netflix}
            \item{Generated recommendations daily to personalize email, app notifications and Billboard – the large banner on Netflix homepage}
          \end{itemize}
        \item{Wrote the recommendation algorithm to cold-start new titles with little metadata and no play history}
        \item{Improved Billboard recommendation algorithm to balance impressions among competing titles while maximizing streaming hours}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {First Engineer, Algorithm Engineering Manager} % Title
    {Drawbridge Inc.} % Organization
    {San Mateo, CA} % Location
    {Jan. 2011 - Feb. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Created Drawbridge's first Device Graph to statistically connect anonymized ids of the same user across multiple devices}
          \begin{itemize}[label=$\circ$]
            \item{Achieved over 60\% precision on a partner-provided test dataset}
          \end{itemize}
        \item{Designed and built Drawbridge’s batch data pipeline using Hadoop, Hive, Pig and Oozie to process billions of events in
terabytes of data daily}
        \item{Managed a team of three engineers machine learning building models to:}
          \begin{itemize}[label=$\circ$]
            \item{Click-through rate (CTR) and conversion rate (CVR) prediction and optimization}
            \item{Loss prevention – to flag, stop and alert for ad groups and campaigns where losses, differences between predicted and actual revenues, exceed alert thresholds}
            \item{User behavior, demographic and geographic feature extraction and extrapolation}
          \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Title
    {Announce Media Inc. \bodyfontlight\emph{(Answers.com)}} % Organization
    {Mountain View, CA} % Location
    {Jun. 2010 - Dec. 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Architected and launched Announce Media’s first Hadoop application to parallelize, scale and automate keyword evaluation for the company's core business of search engine marketing}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Title
    {AdMob Inc. \bodyfontlight\emph{(acquired by Google, Inc.)}} % Organization
    {San Mateo, CA} % Location
    {May 2008 - May 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Built and Maintained Unique User (UU) service, a real-time system keeping track of ad impressions and clicks per UU throughout the hyper-growth phase of the early mobile web}
        \item{Created Hadoop jobs to compute UU statistics across geographic and demographic dimensions}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Title
    {Yahoo! Inc.} % Organization
    {Sunnyvale, CA} % Location
    {Sep. 2005 - Apr 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Developed ad-serving, link-tracking, AB testing, location-based personalization and backend for core modules such as RSS, Personal Assistant, Weather, Scoreboard, Mail and TV modules to My Yahoo!}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
