%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Vice President, Data} % Title
  {Lightspeed Venture Partners} % Organization
  {Menlo Park, CA} % Location
  {Jan. 2022 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item{Leading the efforts in scaling Lightspeed's data platform and driving its adoption across the firm}
      \begin{itemize}[label=$\circ$]
        \item{Lightspeed's data platform tracks over 3.8 million companies and 270 million people to search for investment opportunities}
        \item{Our automated data room diligence tool reduces the time to perform due diligence on a company from days to less than 30 minutes}
        \item{Lightspeed data team was voted as one of the top 20 most data driven venture capital funds by peers in Data Driven VC Landscape Report 2 years in a row for 2023 and 2024}
      \end{itemize}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Director of Engineering/Founding Member of Lightspeed's Data Team} % Title
  {} % Organization
  {} % Location
  {Jan. 2019 - December 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item{Led the Data Engineering team at Lightspeed to create a data platform that powers deal sourcing, diligence and portfolio support in venture capital investing}
      \begin{itemize}[label=$\circ$]
        \item{Built scalable data infrastructure to onboard datasets, generate features, train and test machine learning models}
        \item{Created internal tools to help track and analyze relationships and signals on future investment opportunities and candidates}
        \item{Worked cross-functionally with investors and operations teams to improve the quailty of data models and automate business processes}
      \end{itemize}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Machine Learning \& Intelligence Staff Software Engineer, Autonomous Vehicle Division} % Title
  {Lyft Inc.} % Organization
  {San Francisco, CA} % Location
  {Jun. 2018 - Jan. 2019} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item{Built a Kubernetes-based machine learning pipeline to easily iterate on Tensorflow and PyTorch computer vision models to build High Definition maps}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Staff Software Engineer/Engineering Lead} % Title
  {} % Organization
  {} % Location
  {Aug. 2017 - May 2018} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item{Led a team of engineers to rebuild Lyft's live traffic profile estimation pipeline using PySpark, reducing its overall latency from hours to less than 30 minutes --- the pipeline produced traffic models simulating real-time traffic conditions based on recently-live Lyft rides and served as a critical input to Lyft's ETA estimation models}
      \item{Collaborated with ETA Data Science team to reduce Lyft's ETA estimation error rate by 5\%}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Principal Software Engineer/Engineering Lead} % Title
  {Walmart Labs} % Organization
  {Sunnyvale, CA} % Location
  {Aug. 2016 - Apr. 2017} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item{Led a team of engineers to re-architect the Walmart Ad Exchange (WMX) platform on Apache Spark to drive smart and responsive ad-targeting based on Walmart’s unique offline+online datasets}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Senior Software Engineer} % Title
  {Netflix Inc.} % Organization
  {Los Gatos, CA} % Location
  {Aug. 2014 - Jul. 2016} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item{Built and launched the first production-grade machine learning pipeline on Apache Spark at Netflix to:}
      \begin{itemize}[label=$\circ$]
        \item{Enabled rapid development of recommendation algorithms for movies and TV shows}
        \item{Generated daily personalized recommendations to power email, push notifications and Billboard --- the large banner above the fold on Netflix homepage}
      \end{itemize}
      \item{Wrote the recommendation algorithm to cold-start new titles with little metadata and no play history}
      \item{Improved Billboard recommendation algorithm to balance impressions among competing titles while maximizing streaming hours}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {First Engineer, Algorithm Engineering Manager} % Title
  {Drawbridge Inc. \bodyfontlight\emph{(acquired by LinkedIn)}} % Organization
  {San Mateo, CA} % Location
  {Jan. 2011 - Feb. 2014} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item{Created Drawbridge's first Device Graph to statistically connect anonymized ids of the same user across multiple devices}
      \begin{itemize}[label=$\circ$]
        \item{Achieved over 60\% precision on a partner-provided test dataset}
      \end{itemize}
      \item{Designed and built Drawbridge’s batch data pipeline using Hadoop, Hive, Pig and Oozie to process daily billions of events in terabytes of data}
      \item{Managed a team of three engineers building machine learning models for:}
      \begin{itemize}[label=$\circ$]
        \item{Click-through rate (CTR) and conversion rate (CVR) prediction and optimization}
        \item{Loss prevention --- to flag, stop and alert for ad groups and campaigns where losses, differences between predicted and actual revenues, exceed alert thresholds}
        \item{User behavior, demographic and geographic feature extraction and extrapolation}
      \end{itemize}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Senior Software Engineer} % Title
  {Announce Media Inc. \bodyfontlight\emph{(Answers.com)}} % Organization
  {Mountain View, CA} % Location
  {Jun. 2010 - Dec. 2010} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item{Architected and launched Announce Media’s first Hadoop application to parallelize, scale and automate keyword evaluation for the company's core business of search engine marketing}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Software Engineer} % Title
  {AdMob Inc. \bodyfontlight\emph{(acquired by Google)}} % Organization
  {San Mateo, CA} % Location
  {May 2008 - May 2010} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item{Built and maintained Unique User (UU) service, a real-time system keeping track of ad impressions and clicks per UU throughout the hyper-growth phase of the early mobile web}
      \item{Created Hadoop jobs to compute analytics of UU data in AdMob's advertising network}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Software Engineer} % Title
  {Yahoo! Inc.} % Organization
  {Sunnyvale, CA} % Location
  {Sep. 2005 - Apr 2008} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item{Developed ad-serving, link-tracking, A/B testing, location-based personalization and backend for core modules such as Mail, RSS, Scoreboard, TV, Weather and Personal Assistant modules to My Yahoo!}
    \end{cvitems}
  }

  %---------------------------------------------------------
\end{cventries}
